
%----------------------------------------------------------
%                    Arunaksha Talukdar
%----------------------------------------------------------

\newpage

\section{Front-end of Code-Area}
The aim of the module is to develop the Frontend User Interaction module of Code-Area.

\subsection{Schema}
The website consist of hierarchical structure of linking of webpages as follow:
homepage , login page + about or Website Description , contestlist , contesthost , contest page , problem page , Rankboard.

\subsubsection{Homepage}
\begin{itemize}

\item Login region: Which verifies the user’s identification and grant’s further functionalities of the system.
\item About region: Describes a brief intro of the platform ,functionalities and suppotable code Formats.
\item Loginbox: Consist of userID, password entry box and Submit button handled by user authentication Module.

\end{itemize}

\subsubsection{Contestlist}
The ongoing contest at the moment or about to happen (With countdown time)

\subsubsection{Contesthost}
Raising a problem and Describing about it with the following functionalities supportable:
\begin{itemize}
\item Problem name 
\item Problem Description
\item Scores Description
\item Note box : regarding time limit , input limit
\item Save button: To Confirm and proceed.
\item Sample input , expected output with description
\end{itemize}

\subsubsection{Contestpage}
The main Contest page includes : Countdown timer till completion , Complete Problem Description ,Test cases with expected output. 

\subsubsection{Problem page}
\begin{itemize}
\item Short Problem descrition with Sample input ,expected output dialog box
\item Code input Submission Frame output managed by JUDGE module. With a management of
Code sumbimtted and rank in rankboard by DATABASE module.
\item Submit box: Link to Rankboard , and final submission of code.
\end{itemize}

\subsubsection{Rankboard}
\begin{itemize}
\item Shows rank of Coders (On basis of JUDGE module)
\item Resubmit Button: Option to revisit the problem and Modify it and submit without altering the previous Submit{No limit to Submissions }.
\end{itemize}
%----------------------------------------------------------